I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-10-26 paper_io_sim.tex
Update single-threaded exps notebooks
Update memprof figures and README

			\begin{figure*}
			\centering
			\begin{subfigure}{\columnwidth}
				\centering
   				\includegraphics[width=\columnwidth]{result/single/figures/single_comp_sep_20gb.pdf}
   				\caption{20GB input file}	\label{fig:single_memprof_20gb}
			\end{subfigure}	
			\begin{subfigure}{\columnwidth}
				\centering
   				\includegraphics[width=\columnwidth]{result/single/figures/single_comp_sep_100gb.pdf}
   				\caption{100GB input file}	\label{fig:single_memprof_100gb}
			\end{subfigure}	
			\caption{Memory profiling results with different input file sizes}
			\label{fig:single_memprof}	
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/errors.pdf}
			\end{subfigure}
			\caption{Simulation errors with different input file sizes}
			\label{fig:single_error}	
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
			\end{subfigure}	
			\label{fig:single_cache}
   			\caption{Amount of file data in cache after each I/O activity with 100GB of input}
			\end{figure*}

@@

			In this experiment, the results is analyzed with the average I/O time of concurrent pipelines.
			The results from real execution and simulation are presented in Figure~\ref{fig:multi_result}.

			The Figure~\ref{fig:multi_readtime} shows that as the number of pipelines 
			increases, the average read time raises accordingly because the amount of data 
			increases but memory and disk bandwidths are fixed and shared between pipelines. 
			In comparison with original WRENCH, the result from WRENCH with page cache are closer 
			to reality. 
			Especially, when it comes to the average write time 
			(shown in Figure~\ref{fig:multi_writetime}), 
			although the trend in reality is more complex, our WRENCH with page cache 
			simulator can still capture it and share the same pattern with 
			the real execution, when they gradually increase before surging 
			with the same slope after the number of pipelines reaches 10. 
			This can be explained that with less than 10 concurrent pipelines, 
			the page cache is not saturated, so all files can be written entirely to 
			cache with memory bandwidth in a short time. 
			After the page cache is saturated with dirty data (at around 
			10 concurrent pipelines in this experiment), this dirty data needs 
			to be flushed in order to make space available for writing new data to cache. 
			This dirty data is flushed to disk with disk bandwidth, which is much  
			slower than memory bandwidth. 
			The more pipelines we have, the more data needs to be written, the more data 
			needs to be flushed, leading to a sharper increase in the average write time.

>>>>

			\begin{figure*}
			\centering
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_memprof.pdf}
			\end{subfigure}
			\caption{Memory profiling results with different input file sizes}
			\label{fig:single_memprof}	
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_errors.pdf}
			\end{subfigure}
			\caption{Simulation errors with different input file sizes}
			\label{fig:single_error}	
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
			\end{subfigure}	
			\label{fig:single_cache}
   			\caption{Amount of file data in cache after each I/O activity with 100GB of input}
			\end{figure*}

@@

			In this experiment, the results are analyzed in terms of average I/O time 
			of concurrent pipelines shown in Figure~\ref{fig:multi_local}.

			As is shown in the figure, when the number of pipelines increases, 
			the average read time raises accordingly because the amount of data 
			increases but memory and disk bandwidths are fixed and shared between pipelines. 
			In comparison with original WRENCH, the result from WRENCH with page cache are closer 
			to reality. 
			Especially, when it comes to the average write time, 
			although the trend in reality is more complex, our WRENCH with page cache 
			simulator can still capture the pattern in real execution.
			In both, the average write time gradually increases before surging with the 
			same slopes after the number of pipelines reaches 10. 
			This can be explained that with less than 10 concurrent pipelines, 
			the page cache is not saturated, so all files can be written entirely to 
			cache with memory bandwidth in a short time. 
			After the page cache is saturated with dirty data (at around 
			10 concurrent pipelines in this experiment), this dirty data needs 
			to be flushed in order to make space available for writing new data to cache. 
			This dirty data is flushed to disk with disk bandwidth, which is much  
			slower than memory bandwidth. 
			The more pipelines we have, the more data needs to be written, the more data 
			needs to be flushed, leading to a sharper increase in the average write time.
